Score-based tests of measurement invariance: Use in practice

### 2014-03-05 frontiers/IMPSpres.Rnw
update the application part.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@326 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass{beamer}
\setbeamertemplate{caption}[numbered]
\usepackage{beamerthemeSzeged,graphics,amsmath,bm,booktabs}
\usepackage{tikz}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usefonttheme{serif}
% Seems necessary for texlive 2012?
\usetikzlibrary{arrows}

@@

\renewcommand{\baselinestretch}{1.1}

@@

  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("ordmax", "ordwmax", "catdiff"),
  labels = c("maxLM_o", "WDM_o", "LM_uo"))
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=", levels(sim2$nlevels), sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=", levels(sim2$nobs), sep="")
  parlabs <- c(expression(lambda[11]), expression(phi[12]), 
               expression(psi[11]), expression(mu[11]),
	       expression(list(lambda[11], ldots, lambda[62])), 
               expression(list(psi[11], ldots, psi[66])),
               expression(list(mu[11], ldots, mu[66])))
  levels(sim2$pars) <- c("Loading1", "Covariance", "Error1", "Intercept1", 
                         "All Loadings", "All Errors", "All Intercepts")
@

@@

\section{Conclusion}
\section{Application}
\begin{frame}[fragile]
\frametitle{Input data and Fit model}
\begin{enumerate}
 \item Input data
<<data,eval=FALSE>>=
data("YouthGratitude", package = "psychotools")
compcases <- apply(YouthGratitude[, 4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases, ]
@ 
\item Fit restricted model and full model
<<modeest,eval=FALSE>>=
restr <- cfa("f1 =~ gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
  data = yg, group = "agegroup", meanstructure = TRUE,
  group.equal = "loadings")

full <- cfa("f1 =~ gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
  data = yg, group = "agegroup", meanstructure = TRUE)
@ 
\end{enumerate}
\end{frame}

%--------------------------------------------------------------------------
%TODO: reset counter for enumerate.
\begin{frame}
  \item fff
\end{frame}
\end{document}

>>>>

\documentclass{beamer}
\setbeamertemplate{caption}[numbered]
\usepackage{beamerthemeSzeged,graphics,amsmath,bm,booktabs}
\usepackage{tikz}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{enumitem}
\usefonttheme{serif}
% Seems necessary for texlive 2012?
\usetikzlibrary{arrows}

@@

\renewcommand{\baselinestretch}{1.1}
\newcounter{tmpc}

@@

  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("ordmax", "ordwmax", "catdiff"),
  labels = c("maxLM_o", "WDM_o", "LM_uo"))
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=", levels(sim2$nlevels), sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=", levels(sim2$nobs), sep="")
  parlabs <- c(expression(lambda[11]), expression(phi[12]), 
               expression(psi[11]), expression(mu[11]),
	       expression(list(lambda[11], ldots, lambda[62])), 
               expression(list(psi[11], ldots, psi[66])),
               expression(list(mu[11], ldots, mu[66])))
  levels(sim2$pars) <- c("Loading1", "Covariance", "Error1", "Intercept1", 
                         "All Loadings", "All Errors", "All Intercepts")

data("YouthGratitude", package = "psychotools")
compcases <- apply(YouthGratitude[, 4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases, ]

restr <- cfa("f1 =~ gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
  data = yg, group = "agegroup", meanstructure = TRUE,
  group.equal = "loadings")

set.seed(1090)
wdmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4,
  vcov = "info", functional = "WDMo")

if(file.exists("maxLMo.rda")){
  load("maxLMo.rda")
} else {
  RNGkind(kind = "default", normal.kind = "default")
  set.seed(1090)
  maxLMo <- ordL2BB(yg$agegroup, nproc = 4)
  save(maxLMo, file = "maxLMo.rda")
}
maxlmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4,
  vcov = "info", functional = maxLMo)

@

@@

\section{Conclusion}
\section{Application}
\begin{frame}[fragile]
\frametitle{Procedures of Application}
\begin{enumerate}
 \item Input data
\asuivre
\end{enumerate}
<<data,eval=FALSE>>=
data("YouthGratitude", package = "psychotools")
compcases <- apply(YouthGratitude[, 4:28], 1, function(x) all(x %in% 1:9))
yg <- YouthGratitude[compcases, ]
@

\end{frame}

%--------------------------------------------------------------------------
\begin{frame}[fragile]
\frametitle{Procedures of Application}
\begin{enumerate}
\item Fit your model
\end{enumerate}
 <<modeest,eval=FALSE>>=
  restr <- cfa("f1 =~ gq6_1 + gq6_2 + gq6_3 + gq6_4 + gq6_5",
  data = yg, group = "agegroup", meanstructure = TRUE,
  group.equal = "loadings")
@

\end{frame}
%--------------------------------------------------------------------------
\begin{frame}[fragile]
\frametitle{Procedures of Application}
\begin{enumerate}[resume]
  \item Test if M.I. is violated.
\end{enumerate}
<<sctest-ord2, eval=FALSE>>=
wdmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = "WDMo",  plot = TRUE, ylim = c(0, 3.2),
  xlab = "Age group", ylab = "Weighted test statistics")
maxlmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4,
  vcov = "info", functional = "maxLMo",  plot = TRUE, ylim = c(0, 14),
  xlab = "Age group", ylab = "LM statistics",
  main = expression(maxLM[o]), boundary = list(col = 1, lty = 2))
@

\end{frame}

\begin{frame}
  \frametitle
\begin{figure}
\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic 
  (left panel) and the $\max\mathit{LM}_o$ statistic (right panel).}
\label{fig:ordres}
<<sctest-ord-graphics, fig=TRUE, height=4.5, width=9, echo=FALSE, results=hide>>=

par(mfrow = c(1, 2))
set.seed(1090)
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = "WDMo", plot = TRUE, ylim = c(0, 3.2),
  xlab = "Age group", ylab = "Weighted test statistics",
  main = expression(WDM[o]), boundary = list(col = 1, lty = 2))
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = maxLMo, plot = TRUE, ylim = c(0, 14),
  xlab = "Age group", ylab = "LM statistics",
  main = expression(maxLM[o]), boundary = list(col = 1, lty = 2))
@
\end{figure}
\end{frame}
\end{document}
